Cybersecurity Is Too Important To Be Left To The Specialists

### 2019-01-28 ITiCSE2019.tex
Conclusions

\subsection{Android}
\cite{Fischeretal2017a} looked specifically at the use of resources from Stack Overflow in Android applications. Their key finding was this.
\begin{quote}
We found that 15.4\% of all 1.3 million Android applications
contained security-related code snippets from
Stack Overflow. Out of these 97.9\% contain at least one
insecure code snippet.
\end{quote}
We should note two caveats (in opposite directions). Their labelling was conservative, in that snippets were only labelled as insecure if that was demonstrable, and, for example, mere use of outdated SSL/TLS was not automatically deemed insecure. On the other hand, the insecure snippet might have been used in a way that did not expose the insecurity.

@@

\section{Conclusions}
As regards our research questions, we can make the following comments.
\begin{description}
\item[RQ1]
\item[RQ2]The recommendation in \cite[p. 98]{ACM2013a} that Cybersecurity be taught largely through other Knowledge Areas is, in abstract, a good idea. Indeed, a recnt discussion on Cybersecurity had the aerospace engineers amazed that security was a separate topic: ``for us, safety is present everywhere''.  However, in the current state of education resources (sections \S\ref{sec:SQL}--\ref{sec:Java}) this may be a counsel of perfection.  It is mor eimportant that issues like SQL injection \cite{Drop2019} or correct use of SSL/TLS \cite{Chenetal2019a} be taught somewhere than tthat they not be taught at all.
\item[RQ3]Accreditation (as practised by BCS) is a valuable tool in improving the standard of Cybersecurity teaching, and spreading good practice, and should continue this.
\end{description}

>>>>

\subsection{Android}\label{sec:Android}
\cite{Fischeretal2017a} looked specifically at the use of resources from Stack Overflow in Android applications. Their key finding was this.
\begin{quote}
We found that 15.4\% of all 1.3 million Android applications
contained security-related code snippets from
Stack Overflow. Out of these 97.9\% contain at least one
insecure code snippet.
\end{quote}
We should note two caveats (in opposite directions). Their labelling was conservative, in that snippets were only labelled as insecure if that was demonstrable, and, for example, mere use of outdated SSL/TLS was not automatically deemed insecure. On the other hand, the insecure snippet might have been used in a way that did not expose the insecurity.

@@

\section{Conclusions}
As regards our research questions, we can make the following comments.
\begin{description}
\item[RQ1]The guidelines from both ACM and BCS are good for general education. However, the most important item would seem to be an attitude of caution with respect to both offline (\S\ref{sec:SQL}) and online (\S\ref{sec:Java}--) resources. 
\item[RQ2]The recommendation in \cite[p. 98]{ACM2013a} that Cybersecurity be taught largely through other Knowledge Areas is, in abstract, a good idea. Indeed, a recnt discussion on Cybersecurity had the aerospace engineers amazed that security was a separate topic: ``for us, safety is present everywhere''.  However, in the current state of education resources (sections \S\ref{sec:SQL}--\ref{sec:Java}) this may be a counsel of perfection.  It is more important that issues like SQL injection \cite{Drop2019} or correct use of SSL/TLS \cite{Chenetal2019a} be taught somewhere than tthat they not be taught at all.
\par
We comend the BCS-identified good practice of exploring Cybersecurity via a project, possibly in PCI DSS (\S\ref{sec:PCIDSS}).
\item[RQ3]Accreditation (as practised by BCS) is a valuable tool in improving the standard of Cybersecurity teaching, and spreading good practice, and should continue this.
\end{description}
